## Harjoituskerta 2
```{r}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = rectangle]        
  rec1 [label = 'Luokittelu']
  rec2 [label = 'Järjestys']
  rec3 [label =  'Välimatka']
  rec4 [label = 'Suhde']
  rec5 [label = 'Epäjatkuvat']
  rec6 [label = 'Jatkuvat']
  
  rec7[label = 
    <
    <br/> &#8226; Frekvenssit <br ALIGN = 'LEFT'/> &#8226; Sijaintiluvut: moodi, mediaani<br ALIGN = 'LEFT'/> &#8226; Pylväsdiagrammi <br ALIGN = 'LEFT' />
    >
]

rec8[label = 
    <
    <br/> &#8226; Sijaintiluvut: moodi, mediaani, keskiarvo<br ALIGN = 'LEFT'/> &#8226; Hajontaluvut: vaihteluväli, keskihajonta, vinous, huipukkuus<br ALIGN = 'LEFT'/> &#8226; Histogrammi <br ALIGN = 'LEFT' />
    >
]


  
  # edge definitions with the node IDs
  rec1 -> rec5; rec2 -> rec5; rec3 -> rec6; rec4 -> rec6;
  rec5 -> rec7; rec6 -> rec8
  }",
  height = 500)
```


### Frekvenssijakaumat

Muuttujan frekvenssijakaumaa voi tutkia funktiolla table

```{r, echo=TRUE}
table(df$F11, useNA = "always")
```


### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
