## Harjoituskerta 2

```{r}
taul1 %>% kable(col.names = NULL) %>% 
  row_spec(1, bold = TRUE, color = "white", background="#077d9e") %>% 
  row_spec(seq(2,nrow(taul1),2), background="#ccd8df") %>% 
  row_spec(seq(3,nrow(taul1),2), background="#e7ecf0") %>% 
  row_spec(3, bold=TRUE, font_size = 17) %>% 
  kableExtra::kable_styling()
```


<center>

```{r, fig.align='center'}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB, 
  label=
  <
  <br/> Jakauman tarkastelu  <br/>
    <font point-size='30'>Minkälainen muuttuja on kyseessä?</font>
  <br/>
  >, labelloc=top,
  fontsize = '40', margin='1.5']
  
  node [shape = rectangle, style='filled', fontname = Helvetica, fontsize = '20']        
  rec1 [label = 'Luokittelu', fillcolor='#077d9e', fontcolor='white']
  rec2 [label = 'Järjestys', fillcolor='#077d9e', fontcolor='white']
  rec3 [label =  'Välimatka', fillcolor='#077d9e', fontcolor='white']
  rec4 [label = 'Suhde', fillcolor='#077d9e', fontcolor='white']
  rec5 [label = 'Epäjatkuvat', fillcolor='#ccd8df']
  rec6 [label = 'Jatkuvat', fillcolor='#ccd8df']
  
  rec7[label = 
    <
    <br/> &#8226; Frekvenssit <br ALIGN = 'LEFT'/> &#8226; Sijaintiluvut: moodi, mediaani<br ALIGN = 'LEFT'/> &#8226; Pylväsdiagrammi <br ALIGN = 'LEFT' />
    >, fillcolor='#e7ecf0'
]

rec8[label = 
    <
    <br/> &#8226; Sijaintiluvut: moodi, mediaani, keskiarvo<br ALIGN = 'LEFT'/> &#8226; Hajontaluvut: vaihteluväli, keskihajonta, vinous, huipukkuus<br ALIGN = 'LEFT'/> &#8226; Histogrammi <br ALIGN = 'LEFT' />
    >, fillcolor='#e7ecf0'
]


  
  # edge definitions with the node IDs
  rec1 -> rec5; rec2 -> rec5; rec3 -> rec6; rec4 -> rec6;
  rec5 -> rec7; rec6 -> rec8
  }",
  height = 500)
```

</center>

### Frekvenssijakaumat

Muuttujan frekvenssijakaumaa voi tutkia funktiolla **table**. Prosenttijakauman saa
näkymään funktiolla **prop.table**, jolle annetaan argumentiksi table-objekti.

```{r, echo=TRUE, out.width="100%"}
frekvenssitaulu <- table(df$F11, useNA = "always")
frekvenssitaulu
prop.table(frekvenssitaulu)

```

### Pylväsdiagrammi

```{r, echo=TRUE, out.width="100%"}
# Muutetaan kuvan marginaaleja
par(mar=c(10, 4, 4, 4))
# Jaetaan merkkijonot useammalle riville, niin näkyvät paremmin kuvassa
levels(df$F11) <- str_wrap(levels(df$F11), 20)

frekvenssitaulu <- table(df$F11, useNA = "always")
# las-parametri vaihtaa x-akselin labeleiden suunnan, space-parametrilla muutetaan
# pylväiden etäisyyksiä, cex.names-parametrilla muutetaan x-akselin tekstin kokoa
barplot(frekvenssitaulu, las = 2, space = c(0.5), cex.names = 0.75)
```


### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
